An enhancer code compendium of early human neuronal and neural crest development

### 2025-04-08 manuscript.tex
Intro: compendium

@@

In this study, we address these limitations by determining the enhancer-codes of cell types and cell states generated by human neural tube organoids, 
a model system for early human neuronal and neural crest development\cite{abdelfattahActuationEnhancesPatterning2021}
and compare these codes to those of of the head of a four weeks post conception human embryo.
Through these comparisons we confirm the enhancer-code paradigm, 
but also provide a counter examples specifically related to the enhancer-code underlying anterior-posterior patterning.
\par

>>>>

%Context
Enhancers encode cell types and cell states using 
%need
%task
%results
%conclusion
%implication

@@

In this study, we address these limitations by building an enhancer-codes compendium of cell types and cell states generated by human neural tube organoids, 
a model system for early human neuronal and neural crest development\cite{abdelfattahActuationEnhancesPatterning2021}.
We compare this compendium to that of the head of a four weeks post conception human embryo.
Through these comparisons we confirm the enhancer-code paradigm, 
but also provide a counter examples specifically related to the enhancer-code underlying anterior-posterior patterning.
\par
